\label{paper1:references}
\begin{thebibliography}{99}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%% START 9_references.tex %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\item Braidotti, R. (2010). Writing. In: A. Parr (Ed.). \textit{The Deleuze Dictionary}, Edinburgh: Edinburgh University Press, 309-311.   
\item Ingold, T. (2000). \textit{The Perception of the Environment: Essays on livelihood, dwelling and skill}. London \& New York: Routledge. 
\item Latour, B. (2004). How to talk about the Body. The normative dimension of science studies. \textit{Body and Society}, 10 (2/3), pp. 205-229.  
\item Law, J. (2004). \textit{After method: Mess in social science research}. New York: Routledge. 
\item Meier, N. \& Wegener, C. (2016a). Writing with Resonance. \textit{Journal of Management Inquiry}. (Ahead of print). \url{http://journals.sagepub.com/doi/abs/10.1177/1056492616673911}.
\item Meier, N. \& Wegener, C. (2016b). Engaging with the process of writing can connect researcher and reader and foster real innovation and impact. Blogpost, London School of Economics Impact Blog. (\url{http://blogs.lse.ac.uk/impactofsocialsciences/2016/11/04/engaging-with-the-processof-writing-can-connect-researcher-and-reader-and-foster-real-innovation-and-impact}).
\item Rosa, H. (2014). Harmut Rosa talks about his concept of “Resonance.” Leipzig: Degrowth Conference. Retrieved from \url{http://www.lyrics-youtube.com/lyrics/harmut-rosa-talks-about-his-concept-of-resonance-degrowth-leipzig-2014-XCLPpU0hSUw}.
\item Rosa, H. (2016). \textit{Resonanz --- Eine Soziologie der Weltbeziehung}. Berlin: Suhrkamp Verlag. 
\item Wikan, U. (2013). \textit{Resonance: Beyond the Words}. Chicago: The University of Chicago Press. 
\item Wikan, U. (1992). \textit{Beyond words: the power of resonance}. American Ethnologist 19: 460–82.

%##################################################################################################################################################################################################################################
\end{thebibliography}